Parsimonious Representation of Nonlinear Dynamical Systems using Diffusion Maps: A Chemotaxis Case Study

### 2014-12-12 chemotaxis/paper/draft1.tex
updated chemotaxis paper
updated chemotaxis paper and figures

\subsection{Observers}
Add physical examples, and Amit's bi-spectrum, scattering....

Cite PNAS, stating that the histograms are good since they linearize any noise.

\subsection{Metric}
Euclidean (not good, especially for histograms), Mahalanobis (good, cite PNAS, since it noise robust). Here we use EMD since it is multiscale.
Stability and regularity issues.

\section{Identify the principal components}

@@

\includegraphics[height=3in]{swissroll1_evals}
\includegraphics[height=3in]{swissroll2}\\
\includegraphics[height=2in]{swissroll1_cv}
\includegraphics[height=2in]{swissroll2_cv}\\
\includegraphics[height=3in]{swissroll1_color1}
\includegraphics[height=3in]{swissroll2_color1}\\
\includegraphics[height=3in]{swissroll1_color2}
\includegraphics[height=3in]{swissroll2_color2}

For first case: $\lambda_1 = 0.9982$, $\lambda_2 = 0.9959$

For second case: $\lambda_1 = 0.9977$, $\lambda_5 = 0.9652$.

@@

@@

\includegraphics[height=2in]{lle_errors1}
\includegraphics[height=2in]{lle_errors2}

\includegraphics[height=2in]{lle_evals1}
\includegraphics[height=2in]{lle_evals2}

\includegraphics[height=2in]{lle_embed1_1}
\includegraphics[height=2in]{lle_embed2_2}

\hfill 
\includegraphics[height=2in]{lle_embed1_2}

>>>>

\subsection{Observers}

\begin{itemize}
\item Physical examples (e.g., $\alpha$-carbons for molecules)
\item Amit's bispectrum
\item Scattering transform
\item Cite PNAS, stating that the histograms are good since they linearize any noise. 
\end{itemize}

\subsection{Metric}

\begin{itemize}
\item Euclidean (not good, especially for histograms)
\item Mahalanobis (good, cite PNAS, since it noise robust)
\item Here we use EMD since it is multiscale.
\item Emphasize stability and regularity issues.
\end{itemize}

\section{Identifying the Principal Components}

\begin{itemize}
\item Discuss the issues: harmonics
\item Give simple example (Laplacian on strip)
\end{itemize}

@@

\begin{figure}
%
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[height=1.5in]{swissroll1}\\
\includegraphics[height=1.5in]{swissroll1_evals}\\
\includegraphics[height=1.5in]{swissroll1_color1}\\
\includegraphics[height=1.5in]{swissroll1_color2}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[height=1.5in]{swissroll2} \\
\includegraphics[height=1.5in]{swissroll2_evals} \\
\includegraphics[height=1.5in]{swissroll2_color1}\\
\includegraphics[height=1.5in]{swissroll2_color2}
\caption{}
\end{subfigure}
%
\caption{}
\end{figure}

%For first case: $\lambda_1 = 0.9982$, $\lambda_2 = 0.9959$

%For second case: $\lambda_1 = 0.9977$, $\lambda_5 = 0.9652$.

@@

\begin{figure}[t]
%
\includegraphics[width=2.5in]{torus1}
\hfill
\includegraphics[height=1.5in]{torus1_evals}\\
%
\includegraphics[width=2.5in]{torus2}
\hfill
\includegraphics[height=1.5in]{torus2_evals}\\
%
\includegraphics[width=2.5in]{torus3}
\hfill
\includegraphics[height=1.5in]{torus3_evals}
%
\caption{}
\end{figure}

@@

\begin{figure}
%
\def\figheight{1.4in}
%
\begin{subfigure}[t]{0.31\textwidth}
\includegraphics[height=\figheight]{chemotaxis1_evals}
\includegraphics[height=\figheight]{chemotaxis1_embed_good}
%\includegraphics[height=1.5in]{chemotaxis1_embed_bad}
\end{subfigure}
%
\begin{subfigure}[t]{0.31\textwidth}
\includegraphics[height=\figheight]{chemotaxis2_evals}
\includegraphics[height=\figheight]{chemotaxis2_embed_good}
\includegraphics[height=\figheight]{chemotaxis2_embed_bad}
\end{subfigure}
%
\begin{subfigure}[t]{0.35\textwidth}
\includegraphics[height=\figheight]{chemotaxis3_evals}
\includegraphics[height=\figheight]{chemotaxis3_embed_good}
\includegraphics[height=\figheight]{chemotaxis3_embed_bad}
\end{subfigure}
%
\caption{}
%
\end{figure}
